Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-22 paper.tex
Removed confusing figure, changed 2 plots to clarify info, implemented changes discussed in office

\begin{figure}
  \centering
  \begin{subfigure}
    \centering
    \includegraphics[width=0.38\textwidth]{figures/system_use.png}
    \caption{The system in use during an experiment. }\label{fig:system-use}
  \end{subfigure}
  \begin{subfigure}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
    \caption{The system layout and control loop. $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation. $K$, $H$ and $P$ are the control, human and sensor blocks respectively. }\label{fig:control-loop}
  \end{subfigure}
\end{figure}

@@

\begin{equation}
  R = r(s, s').
\end{equation}

@@

The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models. The bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$. Since the camera perspectives and absolute distances between the objects in the images are not given, we can only extract the relationships in the basic action terms specified in $\mathbf{A}$, e.g.\ we can only say that object 1 is above object 2, but not how far above. Our simple action-space and grid environment somewhat compensates for the dataset's lack of complexity.

@@

The app was developed on and experimented with an Asus ZenPhone AR\todo{No footers}\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore\footnote{https://developers.google.com/ar/} SDK enabled. No hardware or software modifications were required.

@@

\begin{table}
  \centering
  \caption{A table containing the results for the TAR, number of steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each participant. }\label{tab:results-full}
  \begin{tabular}{cccc}
    \toprule
    Participant & TAR [\%] & Num. Steps & Time [s] \\ \midrule
    %\multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
				 %&			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
    s1 & 94 & 7.2 $\pm$ 5.4 & 29 $\pm$ 22 \\ \midrule
    s2 & 79 & 6.7 $\pm$ 4.8 & 34 $\pm$ 5.1 \\ \midrule
    s3 & 91 & 6.3 $\pm$ 4.9 & 31 $\pm$ 21 \\ \midrule
    s4 & 79 & 6.7 $\pm$ 4.3 & 37 $\pm$ 5.6 \\ \midrule
    s5 & 76 & 7.2 $\pm$ 4.9 & 33 $\pm$ 14 \\ \midrule
    s6 & 60 & 8.2 $\pm$ 5.4 & 24 $\pm$ 10 \\ \midrule
    s7 & 86 & 8.5 $\pm$ 5.8 & 31 $\pm$ 16 \\ \midrule
    s8 & 88 & 5.1 $\pm$ 4.0 & 39 $\pm$ 21 \\ \midrule
    s9 & 98 & 7.2 $\pm$ 5.4 & 39 $\pm$ 18 \\ \midrule
    s10 & 67 & 6.6 $\pm$ 5.4 & 26 $\pm$ 12 \\ \midrule
    \bottomrule                    
  \end{tabular}                    
\end{table}

@@

\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 15-step limit we set and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches. Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present. Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off at higher step-limits. The angled tail at the 15-step limit is interesting to note, however. \todo{WHY}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/cdf_tar_limit.png}
  \caption{The distribution of the TAR as a function of the step limit for a search. }\label{fig:tar-steps}
\end{figure}

@@

The number of waypoints each participant required is fairly evenly spread across all of the participants, with the majority of searches ending at $n < 4 \land n > 13$. The population mean and standard deviation is 6.8 and 5.1 waypoints respectively. This is a reasonable result, since most target objects were placed within approximately 4 grid squares away from the participants' initial looking directions. However, the relatively high standard deviation should be noted and can also be reduced by implementing the automatic recovery mode mentioned previously, and avoiding information-sparse areas.

As expected, the number of steps the simulation required on average to find the target object is less than the participants did during the experiments. The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Figure~\ref{fig:sim-vs-experiment}.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/experiment_vs_simulation.png}
  \caption{A summary of the experiment and simulation steps to target results. }\label{fig:sim-vs-experiment}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}
    \centering
    \includegraphics[width=0.38\textwidth]{figures/system_use.png}
    \caption{The system in use during an experiment. }\label{fig:system-use}
  \end{subfigure}
  \hspace{8mm}
  \begin{subfigure}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
    \caption{The system layout and control loop. $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation. $K$, $H$ and $P$ are the control, human and sensor blocks respectively. }\label{fig:control-loop}
  \end{subfigure}
\end{figure}

@@

\begin{equation}
  R\in r(s, s').
\end{equation}

@@

The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models. The bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$. Since the camera perspectives and absolute distances between the objects in the images are not given, we can only extract the relationships in the basic action terms specified in $\mathbf{A}$, e.g.\ we can only say that object 1 is above object 2, but not how far above. Our simple action-space and grid environment somewhat compensates for the dataset's lack of complexity.

@@

The app was developed on and experimented with an Asus ZenPhone AR running Android version 7.0 with Google's augmented reality toolkit (ARCore) enabled for measurement and device tracking. No hardware or software modifications were required.

@@

\begin{table}
  \centering
  \caption{A table containing the results for the TAR, number of steps and time to target means and standard deviations for each participant. }\label{tab:results-full}
  \begin{tabular}{cccc}
    \toprule
    Participant & TAR [\%] & Num. Steps & Time [s] \\ \midrule
    %\multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
				 %&			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
    s1 & 94 & 7.2 $\pm$ 5.4 & 29 $\pm$ 22 \\ \midrule
    s2 & 79 & 6.7 $\pm$ 4.8 & 34 $\pm$ 5.1 \\ \midrule
    s3 & 91 & 6.3 $\pm$ 4.9 & 31 $\pm$ 21 \\ \midrule
    s4 & 79 & 6.7 $\pm$ 4.3 & 37 $\pm$ 5.6 \\ \midrule
    s5 & 76 & 7.2 $\pm$ 4.9 & 33 $\pm$ 14 \\ \midrule
    s6 & 60 & 8.2 $\pm$ 5.4 & 24 $\pm$ 10 \\ \midrule
    s7 & 86 & 8.5 $\pm$ 5.8 & 31 $\pm$ 16 \\ \midrule
    s8 & 88 & 5.1 $\pm$ 4.0 & 39 $\pm$ 21 \\ \midrule
    s9 & 98 & 7.2 $\pm$ 5.4 & 39 $\pm$ 18 \\ \midrule
    s10 & 67 & 6.6 $\pm$ 5.4 & 26 $\pm$ 12 \\ \midrule
    \bottomrule                    
  \end{tabular}                    
\end{table}

@@

\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 15-step limit we set and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches. Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present. Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off as the step-limit increases.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/cdf_tar_limit.png}
  \caption{The distribution of the TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
\end{figure}

@@

The number of waypoints each participant required is fairly evenly spread across all of the participants, with the majority of searches ending within 4 steps of initialisation or ending. The population mean and standard deviation is 6.8 and 5.1 waypoints respectively. This is a reasonable result, since most target objects were placed within approximately 4 grid squares away from the participants' initial looking directions. However, the relatively high standard deviation should be noted and can also be reduced by implementing the automatic recovery mode mentioned previously, and avoiding information-sparse areas.

%As expected, the number of steps the simulation required on average to find the target object is less than the participants did during the experiments. The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Figure~\ref{fig:sim-vs-experiment}.

%\begin{figure}
  %\centering
  %\includegraphics[width=0.5\textwidth]{figures/experiment_vs_simulation.png}
  %\caption{A summary of the experiment and simulation steps to target results. }\label{fig:sim-vs-experiment}
%\end{figure}
